Pulling oral and IV data from CvTdb

### 2024-08-01 data-raw/pulling_oral_iv_data_cvtdb.Rmd

# This is the final filtering so that the dataset is most consistent with the
# most current near future pull in the new year
cvt_df <- cvt_df %>%
  filter(!is.na(analyte_dtxsid),
         fk_analyzed_chemical_id == fk_dosed_chemical_id, # sometimes test chemical id is not filled out :/
         !(document_id %in% c(38, 65, 110, 112, 46, 31)),
         !(other_study_identifier %in% c("S0916")),
         !(analyte_name_original %in% "methemoglobin"),
         radiolabeled %in% c(NA, FALSE) # Legacy left as NA, other curations explicitly state FALSE
         )
cvt_df %>% distinct(analyte_dtxsid, curation_set_tag) %>% count(curation_set_tag)
cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()

cvt_df %>%
  pull(conc_units_original) %>%
  table()
cvt_df %>%
  filter(conc_units_original %in% "molar percentage") %>% View()

@@

This filtered and transformed dataset has 14,486 observations.

>>>>

# This is the final filtering so that the dataset is most consistent with the
# most current near future pull in the new year
cvt_df <- cvt_df %>%
  filter(!is.na(analyte_dtxsid),
         fk_analyzed_chemical_id == fk_dosed_chemical_id, # sometimes test chemical id is not filled out :/
         !(document_id %in% c(38, 65, 110, 112, 46, 31)),
         !(other_study_identifier %in% c("S0916") & is.na(conc)),
         !(analyte_name_original %in% "methemoglobin"),
         radiolabeled %in% c(NA, FALSE) # Legacy left as NA, other curations explicitly state FALSE
         )
cvt_df %>% distinct(analyte_dtxsid, curation_set_tag) %>% count(curation_set_tag)
cvt_df %>% pull(analyte_dtxsid) %>% unique() %>% length()

cvt_df %>%
  pull(conc_units_original) %>%
  table()
cvt_df %>%
  filter(conc_units_original %in% "molar percentage") %>%

@@

This filtered and transformed dataset has 14,152 observations.
